% LaTeX resume using res.cls
\documentclass[line]{res}
\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
\setlength{\topmargin}{-0.4in}  % Start text higher on the page 
\setlength{\textheight}{11in}  % increase textheight to fit more on a page
\setlength{\headsep}{0.2in}     % space between header and text
\setlength{\headheight}{10pt}   % make room for header
\usepackage{fancyhdr}  % use fancyhdr package to get 2-line header

\begin{document}
\name{\LARGE{Sofya Mulenok}}
% \address used twice to have two lines of address
\address{mulenoksv@gmail.com or (415)-359-3454}

\begin{resume}
\pagestyle{empty}
\section{Experience}
    \textbf{Data Analyst/Specialist} \hfill December 2016 - present\\
    Traackr Inc, San Francisco, CA
    \begin{itemize} \itemsep -2pt
    \item Expanded coverage of Traackr to gaming vertical.
    \item Created tests and quality guidelines for language support; helped launch support for Japanese, Korean, Russian, Greek, Indonesian languages.
    \item Researched and helped implement Traackr integrations with Twitch, StackOverflow, Reddit.
    \item Supporting teams (Customer Success, Marketing, Professional Services, Sales, Engineering, etc.) with data-driven insights
    \item Performing a variety of RnD and maintenance work, such as investigating and testing APIs for integration, creating solutions for data issues, informing the design of data products and reports (using Python, SQL, MongoDB queries).
    \end{itemize}

    \textbf{Search Data Specialist} \hfill December 2015 - December 2016 \\
    IAC Applications, Oakland, CA
    \begin{itemize} \itemsep -2pt
    \item Supervised data evaluation tasks for a team of language specialists.
    \item Created guidelines for, assigning, and performing data evaluation tasks aimed at improving quality and performance of various search products, e.g. "related search", "smart answers", etc.
    \item Supported product team with insights from logs and content databases (querying with SQL Workbench and Microsoft SQL Server).
    \item Automated data collection and evaluation tasks with Python scripts.
    \end{itemize}
    
    \textbf{Knowledge Engineer, International Business} \hfill January 2013 - December 2015 \\
    IAC Search and Media (Ask.com), Oakland, CA
    \begin{itemize} \itemsep -2pt
    \item In cooperation with product and engineering teams, launched the Smart Answer product of Ask.com (similar to Google's knowledge graph) on the international websites.
    \item Launched and maintained partner and editorial content on the US and international Ask.com websites (from making data-driven decisions to content development and managing content database, QA, release).
    \item Automated data scraping and database population tasks with Python scripts.
    \end{itemize}

    \textbf{Localization Specialist, Russian language} \hfill July 2012 - January 2013 \\
    Ask.com, Oakland, CA
    \begin{itemize} \itemsep -2pt
    \item Localized UI into Russian, translated and tested the Russian version of the website.
    \item Evaluated quality of search products on Ask.com; evaluated SEM keyword buys and ad copy for compliance and linguistic accuracy.
    \end{itemize}

\section {Additional Language Skills}
    \textbf{Russian:} native/bilingual
    \textbf{Japanese:} limited working proficiency

\section{Strongest Tools / Skills}
    \textbf{Programming languages:} Python \\
    \textbf{Administration:} Git, familiar with bash \\
    \textbf{Databases:}  SQL, MS SQL Server, SQLite, MongoDB\\
    \textbf{Web development:} HTML, JSON, basic JavaScript \\

\section{Education}
    \textbf{5-year degree (equivalent to MA). in Linguistics and Translation} \hfill June 2008 \\
    Tomsk Polytechnic University, Tomsk, Russia, \textit{with honors}

\end{resume}
\end{document}
